Insert the article title here

### 2018-04-10 writeup/manuscript.tex
Small changes to manuscript
Made some more minor changes. Clarified how the shape/colour assignment was done for the foraging paper

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colours afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

A white digit appeared inside each square. Two targets – a red square and a blue square each with a digit between 2 and 5 – were embedded in every search display. The two target digits were always different, to enable us to distinguish the chosen target. The remaining red, blue and variable squares all contained digits between 6–9. Green squares could contain any digit between 2-9. The location of the targets and distractor within the search display were randomized on each trial.

@@

In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of color and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was counterbalanced across participants (was it?). The procedure was otherwise identical to the feature foraging task.

\subsection{Planned Analysis}

@@

Participants with accuracy more than 3 SD below the group mean were excluded from analyses. For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant’s mean were excluded.

>>>>

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

A white digit appeared inside each square. Two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display. The two target digits were always different, to enable us to distinguish the chosen target. The remaining red, blue and variable squares all contained digits between 6-9. Green squares could contain any digit between 2-9. The location of the targets and distractor within the search display were randomized on each trial.

@@

In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search). Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well. 
\subsection{Planned Analysis}

@@

Participants with accuracy more than 3 SD below the group mean were excluded from analyses. For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant's mean were excluded.
